\documentclass[10pt]{article}

% Allow Unicode input (alternatively, you can use XeLaTeX or LuaLaTeX)
\usepackage[utf8]{inputenc}

\usepackage{microtype,xparse,tcolorbox}
\newenvironment{reviewer-comment }{}{}
\tcbuselibrary{skins}
\tcolorboxenvironment{reviewer-comment }{empty,
	left = 1em, top = 1ex, bottom = 1ex,
	borderline west = {2pt} {0pt} {black!20},
}
\ExplSyntaxOn
\NewDocumentEnvironment {response} { +m O{black!20} } {
	\IfValueT {#1} {
		\begin{reviewer-comment~}
			\setlength\parindent{2em}
			\noindent
			\ttfamily #1
		\end{reviewer-comment~}
	}
	\par\noindent\ignorespaces
} { \bigskip\par }

\NewDocumentCommand \Reviewer { m } {
	\section*{Comments~by~Reviewer~#1}
}
\ExplSyntaxOff
\AtBeginDocument{\maketitle\thispagestyle{empty}\noindent}

% You can get probably get rid of these definitions:
\newcommand\meta[1]{$\langle\hbox{#1}\rangle$}
\newcommand\PaperTitle[1]{``\textit{#1}''}

\title{Response to minor revisions request for manuscript
		NUMA-D-17-00638 \\}
\author{Martin Averseng}
\date{\today}

\begin{document}
	
	I am grateful to the reviewers for their comments on the revised version of this manuscript. Here is an answer to their comments.
	
	\Reviewer{\#1}
	
	I corrected the typo indicated by the reviewer whom I thank for their precise indications. The main comment I wish to answer is the last one:
	\begin{response}
		{The complexity $O(P ^2 \log P+ ...)$ is wrong. The complexity is proportional to the bandwidth.}
	\end{response}	
	I don't understand why the formula is wrong, however, I acknowledge  that I did not provide details on how I obtained this formula. The complexity indicated in the reference is 
	\[O( |I_N| \log |I_N| + |\log \varepsilon|^2\left(N + M\right))\,,\]
	where, as far as I understand, $|I_N| = N_1 N_2$  where $N_1$ and $N_2$ are the bandwidth along each dimension. Here, all the frequencies lie in a circle of radius $\rho_P \approx \pi P = O(P).$ Therefore, the term 
	\[O(|I_N| \log |I_N|)\]
	gives an order $O(P^2 \log(P))$. 
	I included more details on this computation in the new revision of the manuscript. I hope that this is indeed correct and if so, that it is clearer than before. 
	
	\Reviewer{\#2}
	
	I wish to thank the second reviewer for his encouraging comments on my manuscript. I incorporated his suggestions to the revised versions.
	Upon his remark, I used the term "annulus" instead of "ring" and replaced every instance of $\mathcal{R}(a)$ by $\mathcal{A}(a)$. 
	
	  
	
\end{document}